Estimating duration using survival analysis

### 2024-03-22 cis-imperfect-testing.tex
rewrite ch 6

I start by finding the tests that need consideration.
For tractability and simplicity, I consider only tests between the negative tests providing an upper bound on the length of the episode.
By definition (see \cref{E-biology-data:sec:cis-episodes}), these are the tests between $l_{j(i)}^{(b)} - 1$ and $r_{j(i)}^{(e)} + 1$ inclusive.
They are a subset of $\sched_i$, the set of test times for the individual in which episode $i$ occurs.

For tractability, assume that the negative test bounding the start of the episode, on day $l_{j(i)}^{(b)}-1$, is a true negative.
This assumption is reasonable because, since a positive test follows at $r_{j(i)}^{(b)}$, the negative at $l_{j(i)}^{(b)}-1$ is likely early in the infection and the test sensitivity is high early in an infection.
Therefore, this is unlikely to be a false negative because, if the individual was detectable at this time, they are in a period with high test sensitivity.
This true negative occurs with probability 1, and hence does not contribute to the likelihood.
Denote the remaining tests considered as $\sched'_i = \{ t \in \sched_i \ssep r_{j(i)}^{(b)} \leq t \leq r_{j(i)}^{(e)} + 1 \}$, and their results by $\vec{y_{j(i)}} = \{ y_{j(i)}(t) \ssep t \in \sched'_i \}$ where $y_{j(i)}(t) = 1$ if the test on day $t$ is positive and 0 otherwise.

As I assume that there are no false positives, the infection episode must span at least the period $[r^{(b)}_{j(i)}, l^{(e)}_{j(i)}]$ because it starts and ends with a positive test.
This includes all $t \in \sched'_i$ except $t = r_{j(i)}^{(e)}+1$.
Therefore, the test results at times in $\sched_i'$, except the test at $r_{j(i)}^{(e)}+1$, are either true positives or false negatives.

Consider the negative test at $r_{j(i)}^{(e)}+1$, the first negative after the start of the episode which may be a false negative.
It is a false negative if and only if the episode ends after the test, \ie $e_{j(i)} > r_{j(i)}^{(e)}$.
I proceed by considering whether this is the case and considering the case with $b_{j(i)}$ known; $b_{j(i)}$ will later be integrated out.

First, if $e_{j(i)} \leq r_{j(i)}^{(e)}$, meaning that the test at $r_{j(i)}^{(e)}+1$ is a true negative and the end of the episode is interval censored as in the previous chapter.
% In this case, the test at $r_{j(i)}^{(e)} + 1$ is a true negative, as are all other tests not in $\sched'_i$.
The true negative occurs with probability 1, by the assumption of no false positives.
\begin{align}
&p(\vec{y_{j(i)}}, e_{j(i)} \leq r_{j(i)}^{(e)} | b_{j(i)}, p_\text{sens}, \vec{\theta}) \\
&= p(\vec{y_{j(i)}}, l_{j(i)}^{(e)} \leq e_{j(i)} \leq r_{j(i)}^{(e)} | t_i, b_{j(i)}, p_\text{sens}, \vec{\theta}) \\ % &\text{as no false positives}
&= p(\vec{y_{j(i)}} \mid l_{j(i)}^{(e)} \leq e_{j(i)} \leq r_{j(i)}^{(e)}, t_i, b_{j(i)}, p_\text{sens}, \vec{\theta}) p(l_{j(i)}^{(e)} \leq e_{j(i)} \leq r_{j(i)}^{(e)} | t_i, b_{j(i)}, p_\text{sens}, \vec{\theta}) \\
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_{j(i)}(t)} (1 - p_\text{sens})^{(1 - y_{j(i)}(t))} \right) \left( S_{\vec{\theta}}(l_{j(i)}^{(e)} - b_{j(i)} - 1) - S_{\vec{\theta}}(r_{j(i)}^{(e)} - b_{j(i)} - 1) \right)
\label{imperf-test:eq:ll-ei-lt-ri}
\end{align}

Second, if $e_{j(i)} > r_{j(i)}^{(e)}$.
In this case, the test at $r_{j(i)}^{(e)}$ is a false negative, occurring with probability $(1 - p_\text{sens})$.
To avoid having to consider tests after $r_{j(i)}^{(e)}$, which could greatly complicate the likelihood, I model this case as the episode being right censored at $r_{j(i)}^{(e)}$.
Taking the same approach as before:
\begin{align}
&p(\vec{y_{j(i)}}, e_{j(i)} > r_{j(i)}^{(e)} | b_{j(i)}, p_\text{sens}, \vec{\theta}) \\
&= p(\vec{y_{j(i)}} \mid e_{j(i)} > r_{j(i)}^{(e)}, t_i, b_{j(i)}, p_\text{sens}, \vec{\theta}) p(e_{j(i)} > r_{j(i)}^{(e)} | t_i, b_{j(i)}, p_\text{sens}, \vec{\theta}) \\
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_{j(i)}(t)} (1 - p_\text{sens})^{(1 - y_{j(i)}(t))} \right) (1 - p_\text{sens}) S_{\vec{\theta}}(r_{j(i)}^{(e)} - b_{j(i)} - 1)
\label{imperf-test:eq:ll-ei-gt-ri}
\end{align}

These expressions can now be used to form the full replacement for $p_{ia}$, $p'_{ia}$, the likelihood of the data $\vec{y_{j(i)}}$.
First, augment the data with $b_{j(i)}$, and split into the cases just discussed:
\begin{align}
p_{ia}'
&= p(\vec{y_{j(i)}} \mid p_\text{sens}, \vec{\theta}) \\
&= \sum_{b_{j(i)} = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( p(\vec{y_{j(i)}}, e_{j(i)} \leq r_{j(i)}^{(e)} \mid b_{j(i)}, p_\text{sens}, \vec{\theta}) + p(\vec{y_{j(i)}}, e_{j(i)} > r_{j(i)}^{(e)} \mid b_{j(i)}, p_\text{sens}, \vec{\theta}) \right) p(b_{j(i)} \mid p_\text{sens}, \vec{\theta}).
\intertext{Now, substitute in \cref{imperf-test:eq:ll-ei-lt-ri,imperf-test:eq:ll-ei-gt-ri}, then take out the common factor:}
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_{j(i)}(t)} (1 - p_\text{sens})^{(1 - y_{j(i)}(t))} \right) \\ & \ \times \sum_{b_{j(i)} = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( S_{\vec{\theta}}(l_{j(i)}^{(e)} - b_{j(i)} - 1) - S_{\vec{\theta}}(r_{j(i)}^{(e)} - b_{j(i)} - 1) + (1 - p_\text{sens}) S_{\vec{\theta}}(r_{j(i)}^{(e)} - b_{j(i)} - 1) \right) \\ & \ \times p(b_{j(i)} \mid p_\text{sens}, \vec{\theta}) \\
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_{j(i)}(t)} (1 - p_\text{sens})^{(1 - y_{j(i)}(t))} \right) \\ & \ \times \sum_{b_{j(i)} = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( S_{\vec{\theta}}(l_{j(i)}^{(e)} - b_{j(i)} - 1) - p_\text{sens} S_{\vec{\theta}}(r_{j(i)}^{(e)} - b_{j(i)} - 1) \right) p(b_{j(i)} \mid p_\text{sens}, \vec{\theta}).
\label{imperf-test:eq:pia-prime}
\end{align}
Note that if $p_\text{sens} = 1$ then $p_{ia}' = p_{ia}$.

If $\psens$ is fixed (\ie has a point prior) and $p(b_{j(i)} \mid \psens, \vec{\theta}) \propto 1$ (as assumed in \cref{E-perf-test}) then:
\begin{align}
p_{ia}'
&\propto \sum_{b_{j(i)} = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} S_{\vec{\theta}}(l_{j(i)}^{(e)} - b_{j(i)} - 1) - p_\text{sens} S_{\vec{\theta}}(r_{j(i)}^{(e)} - b_{j(i)} - 1).
\label{imperf-test:eq:pia-prime-constant}
\end{align}

@@

Several mechanisms for episodes being undetected were considered when deriving $p_{iu}$ in \cref{perf-test:eq:piu}.
I now consider the additional mechanisms arising due to false negatives.
Specifically, episode $i$ could be undetected if the first test after the $b_{j(i)}$, episode $i$'s start day, is a false negative and then there are no subsequent positive tests.

This false negative would occur at the first test after the infection episode begins, on day $b_{j(i)} + \tau_{\sched_i}(b_{j(i)})$ (see \cref{E-perf-test:sec:model}).
A false negative occurring requires that the episode has not yet ended but a negative still occurs.
The episode has not yet ended at the time of the test if $e_{j(i)} = b_{j(i)} + d_i - 1$ is after the test, that is the duration of the infection $d_i > \tau_{\sched_i}(b_{j(i)})$.
Conditional on the episode having not yet ended, the test result is negative with probability $1 - \psens$.

For there to be no subsequent positive tests, all tests up until day $e_{j(i)}$ are false negatives.
I assume there is a negligible probability of two false negatives.
Therefore, this can only occur if the episode ends before another test.
Denote the number of days between $b_{j(i)}$ and the test following the false negative as $\tau^2_{\sched_i}(b_{j(i)}) \stackrel{\text{def}}{=} \tau_{\sched_i}(\tau_{\sched_i}(b_{j(i)}) + 1)$.
Then, the episode ends before this test if $d_i < \tau^2_{\sched_i}(b_{j(i)})$.

Therefore, this mechanism causes episode $i$ to be undetected if all the following conditions hold.
\begin{enumerate}
    \item The episode would have been detected considering only the mechanisms in \cref{perf-test:eq:piu}. That is $b_{j(i)} > \min(\sched_i)$ and $\tau_{\sched_i}(b_{j(i)}) + b_{j(i)} \leq e_{j(i)}$.
    \item The episode ends in the interval $[\tau_{\sched_i}(b_{j(i)}) + b_{j(i)}, \tau^2_{\sched_i}(b_{j(i)}) + b_{j(i)}]$.
      Note that the lower bound here is exactly the bound on $e_{j(i)}$ in the previous condition.
      Equivalently, $\tau_{\sched_i}(b_{j(i)}) + 1 \leq d_i \leq \tau^2_{\sched_i}(b_{j(i)}) + 1$.
    \item A false negative occurs on day $\tau_{\sched_i}(b_{j(i)}) + b_{j(i)}$. Conditional on the previous condition, this occurs with probability $1 - \psens$.
\end{enumerate}

The probability of this occurring, conditional on $B_{j(i)} = b_{j(i)} > \min(\sched_i)$ is:
\begin{align}
&\prob \left(
    \tau_{\sched_i}(b_{j(i)}) + 1 \leq D_i \leq \tau^2_{\sched_i}(b_{j(i)}) + 1
    \mid b_{j(i)},
\vec{\theta} \right) (1 - \psens) \\
&= \left( S_{\vec{\theta}}(\tau_{\sched_i}(b_{j(i)}) + 1) - S_{\vec{\theta}}(\tau^2_{\sched_i}(b_{j(i)}) + 1) \right) (1 - \psens).
\end{align}
Integrating over $b_{j(i)}$ for $\min \sched_i < b_{j(i)} \leq T$ ($T$ being the last day of the period considered), in the same way as \cref{perf-test:eq:piu}, gives:
\begin{align}
\eta = (1 - p_\text{sens})\frac{1}{T} \sum_{b=\min(\sched_i) + 1}^T \left( S_{\vec{\theta}}(\tau_{\sched_i}(b) + 1) - S_{\vec{\theta}}(\tau^2_{\sched_i}(b) + 1) \right).
\end{align}

Denote the replacement for $p_{iu}$ as $p_{iu}'$.
$p_{iu}'$ is the probability of episode $i$ being undetected, considering both the mechanisms from \cref{E-perf-test} and the new mechanism here.
These mechanisms are mutually exclusive.
Hence, $p_{iu}'$ is the sum of these, $p_{iu}' = p_{iu} + \eta$.
For the posterior density, \cref{E-perf-test:eq:full-posterior}, $1 - p_{iu}'$ is the required quantity.
\begin{align}
1 - p_{iu}'
&= 1 - p_{iu} - (1 - p_\text{sens})\frac{1}{T} \sum_{b=\min(\sched_i) + 1}^T \left( S_{\vec{\theta}}(\tau_{\sched_i}(b) + 1) - S_{\vec{\theta}}(\tau^2_{\sched_i}(b) + 1) \right) \\
&= \frac{1}{T} \sum_{b=\min(\sched_i) + 1}^T \left( p_\text{sens} S_{\vec{\theta}}(\tau_{\sched_i}(b) + 1) + (1 - p_\text{sens}) S_{\vec{\theta}}(\tau^2_{\sched_i}(b) + 1)\right).
\label{imperf-test:eq:pit-prime}
\end{align}

@@

Here, I modify the simulation study in \cref{E-perf-test:sec:simulation-study} to assess several features of the statistical model I proposed in the previous section.
First, the ability to identify the survival function even with false negatives.
Second, the impact of misspecifying $\psens$, such as the assumption that it is constant.
Finally, the impact of the simplifying assumptions made in \cref{imperf-test:sec:modelling} for tractability.
These assumptions are that the negative at $l^{(b)}_i - 1$ is a true negative and that there is a negligible probability of missing an episode due to two false negatives.

>>>>

I start by finding the tests that need consideration for episode $j$.
For tractability and simplicity, I consider only tests between the negative tests providing an upper bound on the length of episode $j$.
By definition (see \cref{E-biology-data:sec:cis-episodes}), these are the tests in individual $i(j)$ between $l_j^{(b)} - 1$ and $r_j^{(e)} + 1$ inclusive.

For tractability, assume that the negative test bounding the start of the episode, on day $l_j^{(b)}-1$, is a true negative.
This assumption is reasonable because, since a positive test follows at $r_j^{(b)}$, the negative at $l_j^{(b)}-1$ is likely early in the infection and the test sensitivity is high early in an infection.
Therefore, this is unlikely to be a false negative because, if the individual was detectable at this time, they are in a period with high test sensitivity.
True negatives occur with probability 1, and hence this test does not contribute to the likelihood.

Denote the set of the remaining test times to consider as $\sched'_{i(j)}$.
$\sched'_{i(j)}$ is the set of times individual $i(j)$ was tested between $l_j^{(b)}$ and $r_j^{(e)} + 1$ inclusive.
Denote their results by $\vec{y}_j = \{ y_{i(j)}(t) \ssep t \in \sched'_{i(j)} \}$ where $y_{i(j)}(t) = 1$ if the test on day $t$ in individual $i(j)$ is positive and 0 otherwise.

As I assume that there are no false positives, the infection episode must span at least the period $[r^{(b)}_j, l^{(e)}_j]$, because this period starts and ends with a positive test.
This includes all $t \in \sched'_{i(j)}$ except $t = r_j^{(e)}+1$.
Therefore, the test results $\vec{y}_j$, except the test at $r_j^{(e)}+1$, are either true positives or false negatives.

Consider the negative test at $r_j^{(e)}+1$, the first negative after the start of the episode which may be a false negative.
It is a false negative if and only if the episode ends after the test, \ie $E_j > r_j^{(e)}$.
I proceed by considering whether this is the case and with $B_j = b$ known.

First, if $E_j \leq r_j^{(e)}$, meaning that the test at $r_j^{(e)}+1$ is a true negative and the end of the episode is interval censored as in the previous chapter.
% In this case, the test at $r_j^{(e)} + 1$ is a true negative, as are all other tests not in $\sched'_{i(j)}$.
The true negative occurs with probability 1, by the assumption of no false positives.
\begin{align}
&\prob(\vec{y_j}, E_j \leq r_j^{(e)} \mid B_j = b, p_\text{sens}, \vec{\theta}) \\
&= \prob(\vec{y_j}, l_j^{(e)} \leq E_j \leq r_j^{(e)} \mid B_j = b, p_\text{sens}, \vec{\theta}) \\ % &\text{as no false positives}
&= \prob(\vec{y_j} \mid l_j^{(e)} \leq E_j \leq r_j^{(e)}, B_j = b, p_\text{sens}, \vec{\theta}) \prob(l_j^{(e)} \leq E_j \leq r_j^{(e)} \mid B_j = b, p_\text{sens}, \vec{\theta}) \\
&= \left( \prod_{t \in \sched'_{i(j)}} p_\text{sens}^{y_{i(j)}(t)} (1 - p_\text{sens})^{(1 - y_{i(j)}(t))} \right) \left( S_{\vec{\theta}}(l_j^{(e)} - b + 1) - S_{\vec{\theta}}(r_j^{(e)} - b + 2) \right)
\label{imperf-test:eq:ll-ei-lt-ri}
\end{align}

Second, if $E_j > r_j^{(e)}$.
In this case, the test at $r_j^{(e)}$ is a false negative, occurring with probability $(1 - p_\text{sens})$.
To avoid having to consider tests after $r_j^{(e)}$, which could greatly complicate the likelihood, I model this case as the episode being right censored at $r_j^{(e)}$.
Taking the same approach as before:
\begin{align}
&\prob(\vec{y_j}, E_j > r_j^{(e)} \mid B_j = b, p_\text{sens}, \vec{\theta}) \\
&= \prob(\vec{y_j} \mid E_j > r_j^{(e)}, B_j = b, p_\text{sens}, \vec{\theta}) \prob(E_j > r_j^{(e)} \mid B_j = b, p_\text{sens}, \vec{\theta}) \\
&= \left( \prod_{t \in \sched'_{i(j)}} p_\text{sens}^{y_{i(j)}(t)} (1 - p_\text{sens})^{(1 - y_{i(j)}(t))} \right) (1 - p_\text{sens}) S_{\vec{\theta}}(r_j^{(e)} - b_j + 2)
\label{imperf-test:eq:ll-ei-gt-ri}
\end{align}

These expressions can now be used to form the full replacement for $p_{ia}$, $p'_{ia}$, the likelihood of the data $\vec{y_j}$.
First, augment the data with $b_j$, and split into the cases just discussed:
\begin{align}
p_{ia}'
=& \prob(\vec{y_j} \mid p_\text{sens}, \vec{\theta}) \\
=& \sum_{b = l_j^{(b)}}^{r_j^{(b)}} \left( \prob(\vec{y_j}, E_j \leq r_j^{(e)} \mid B_j = b, p_\text{sens}, \vec{\theta}) + \prob(\vec{y_j}, E_j > r_j^{(e)} \mid B_j = b, p_\text{sens}, \vec{\theta}) \right) \\
  &\times \prob(B_j = b \mid p_\text{sens}, \vec{\theta}).
\intertext{Now, substitute in \cref{imperf-test:eq:ll-ei-lt-ri,imperf-test:eq:ll-ei-gt-ri} and take out the common factor:}
=& \left( \prod_{t \in \sched'_{i(j)}} p_\text{sens}^{y_{i(j)}(t)} (1 - p_\text{sens})^{(1 - y_{i(j)}(t))} \right) \\ & \ \times \sum_{b = l_j^{(b)}}^{r_j^{(b)}} \left( S_{\vec{\theta}}(l_j^{(e)} - b + 1) - S_{\vec{\theta}}(r_j^{(e)} - b + 2) + (1 - p_\text{sens}) S_{\vec{\theta}}(r_j^{(e)} - b + 2) \right) \\ 
  & \times \prob(B_j = b \mid p_\text{sens}, \vec{\theta}) \\
=& \left( \prod_{t \in \sched'_{i(j)}} p_\text{sens}^{y_{i(j)}(t)} (1 - p_\text{sens})^{(1 - y_{i(j)}(t))} \right) \\
  & \times \sum_{b_j = l_j^{(b)}}^{r_j^{(b)}} \left( S_{\vec{\theta}}(l_j^{(e)} - b_j + 1) - p_\text{sens} S_{\vec{\theta}}(r_j^{(e)} - b_j + 2) \right) \\
  & \times \prob(B_j = b \mid p_\text{sens}, \vec{\theta}).
\label{imperf-test:eq:pia-prime}
\end{align}
Note that if $p_\text{sens} = 1$ then $p_{ia}' = p_{ia}$.

If $\psens$ is fixed (\ie has a point prior) and $p(b_j \mid \psens, \vec{\theta}) \propto 1$ (as assumed in \cref{E-perf-test}) then:
\begin{align}
p_{ia}'
&\propto \sum_{b = l_j^{(b)}}^{r_j^{(b)}} S_{\vec{\theta}}(l_j^{(e)} - b_j + 1) - p_\text{sens} S_{\vec{\theta}}(r_j^{(e)} - b + 2).
\label{imperf-test:eq:pia-prime-constant}
\end{align}

@@

Several mechanisms for episodes being undetected were considered when deriving $p_{iu}$ in \cref{E-perf-test:sec:prob-undetected}.
I now consider the additional mechanisms arising due to false negatives.
Specifically, episode $j$ could be undetected if the first test after $b_j$ is a false negative and then there are no subsequent positive tests.

This false negative would occur at the first test after the infection episode begins, on day $b_j + \tau_{\sched_{i(j)}}(b_j)$ (see \cref{E-perf-test:sec:prob-undetected}).
A false negative occurring requires that the episode has not yet ended but a negative still occurs.
The episode has not yet ended at the time of the test if $e_j = b_j + d_j - 1$ is after the test, that is the duration of the infection $d_j > \tau_{\sched_{i(j)}}(b_j)$.
Conditional on the episode having not yet ended, the test result is negative with probability $1 - \psens$.

For there to be no subsequent positive tests, all tests up until day $e_j$ are false negatives.
I assume there is a negligible probability of two false negatives.
Therefore, this can only occur if the episode ends before another test.
Denote the number of days between $b_j$ and the test following the false negative as $\tau^2_{\sched_{i(j)}}(b_j) \stackrel{\text{def}}{=} \tau_{\sched_{i(j)}}(\tau_{\sched_{i(j)}}(b_j) + 1)$.
Then, the episode ends before this test if $d_j < \tau^2_{\sched_{i(j)}}(b_j)$.

Therefore, this mechanism causes episode $j$ to be undetected if all the following conditions hold.
\begin{enumerate}
    \item The episode would have been detected considering only the mechanisms in \cref{E-perf-test:sec:prob-undetected}. That is $b_j > \min(\sched_{i(j)})$ and $e_j \geq \tau_{\sched_{i(j)}}(b_j) + b_j$.
    \item The episode ends in the interval $[\tau_{\sched_{i(j)}}(b_j) + b_j, \tau^2_{\sched_{i(j)}}(b_j) + b_j]$.
      Note that the lower bound here is exactly the bound on $e_j$ in the previous condition.
      Equivalently, $\tau_{\sched_{i(j)}}(b_j) + 1 \leq d_j \leq \tau^2_{\sched_{i(j)}}(b_j) + 1$.
    \item A false negative occurs on day $\tau_{\sched_{i(j)}}(b_j) + b_j$. Conditional on the previous condition, this occurs with probability $1 - \psens$.
\end{enumerate}

The probability of this occurring, conditional on $B_j = b_j > \min(\sched_{i(j)})$ is:
\begin{align}
&\prob \left(
    \tau_{\sched_{i(j)}}(b_j) + 1 \leq D_j \leq \tau^2_{\sched_{i(j)}}(b_j) + 1
    \mid B_j = b, \vec{\theta} \right) (1 - \psens) \\
&= \left( S_{\vec{\theta}}(\tau_{\sched_{i(j)}}(b_j) + 1) - S_{\vec{\theta}}(\tau^2_{\sched_{i(j)}}(b_j) + 1) \right) (1 - \psens).
\end{align}
Summing over $b_j$ for $\min \sched_{i(j)} < b_j \leq T$ ($T$ being the last day of the period considered), in the same way as \cref{perf-test:eq:piu}, gives:
\begin{align}
\zeta = (1 - p_\text{sens})\frac{1}{T} \sum_{b=\min(\sched_{i(j)}) + 1}^T \left( S_{\vec{\theta}}(\tau_{\sched_{i(j)}}(b) + 1) - S_{\vec{\theta}}(\tau^2_{\sched_{i(j)}}(b) + 1) \right).
\end{align}

Denote the replacement for $p_{iu}$ as $p_{iu}'$.
$p_{iu}'$ is the probability of episode $i$ being undetected, considering both the mechanisms from \cref{E-perf-test} and the new mechanism here.
These mechanisms are mutually exclusive.
Hence, $p_{iu}'$ is the sum of these, $p_{iu}' = p_{iu} + \zeta$.
For the posterior density, \cref{E-perf-test:eq:full-posterior}, $1 - p_{iu}'$ is the required quantity.
\begin{align}
1 - p_{iu}'
&= 1 - p_{iu} - \zeta \\
&= \frac{1}{T} \sum_{b=\min(\sched_{i(j)}) + 1}^T \left( p_\text{sens} S_{\vec{\theta}}(\tau_{\sched_{i(j)}}(b) + 1) + (1 - p_\text{sens}) S_{\vec{\theta}}(\tau^2_{\sched_{i(j)}}(b) + 1)\right).
\label{imperf-test:eq:pit-prime}
\end{align}

@@

Here, I modify the simulation study in \cref{E-perf-test:sec:simulation-study} to assess several features of the statistical model I proposed in the previous section.
First, the ability to identify the survival function even with false negatives.
Second, the impact of misspecifying $\psens$, such as the assumption that it is constant.
Finally, the impact of the simplifying assumptions made in \cref{imperf-test:sec:modelling} for tractability.
These assumptions are that the negative at $l^{(b)}_j - 1$ is a true negative and that there is a negligible probability of missing an episode due to two false negatives.

### 2024-03-22 cis-perfect-testing.tex
rewrite ch 6

By definition (see \cpageref{perf-test:def:admissible}), we have, for any $i \in \set{D}$:
\begin{align}
p_{ia} =& \prob((B_j, E_j) \in \alpha_i \mid \vec{\theta}, i(j) = i) \\
\alpha_i =& \{ (b, e) : l_{j}^{(b)} \leq b \leq r_{j}^{(b)} \wedge l_{j}^{(e)} \leq e \leq r_{j}^{(e)}\}.
\intertext{Omitting the conditioning on $\vec{\theta}$ and $i(j) = i$, this gives:}
p_{ia}
=& \prob \left( l_{j}^{(b)} \leq B_{j} \leq r_{j}^{(b)}, l_{j}^{(e)} \leq E_{j} \leq r_{j}^{(e)} \right) \\
=& \prob \left( l_{j}^{(e)} \leq E_{j} \leq r_{j}^{(e)} \mid l_{j}^{(b)} \leq B_{j} \leq r_{j}^{(b)} \right) \\
   &\times\prob \left( l_{j}^{(b)} \leq B_{j} \leq r_{j}^{(b)} \right) \\
=& \sum_{b = l_{j}^{(l)}}^{r_{j}^{(b)}} \prob \left( l_{j}^{(e)} \leq E_{j} \leq r_{j}^{(e)} \mid B_{j} = b \right) \prob \left(B_{j} = b \right) \\
=& \sum_{b = l_{j}^{(b)}}^{r_{j}^{(b)}} \prob \left( l_{j}^{(e)} - b + 1 \leq D_{j} \leq r_{j}^{(e)} - b + 1 \right) \prob \left(B_{j} = b \right) &\text{by def of $D_{j}$} \\
=& \sum_{b = l_{j}^{(b)}}^{r_{j}^{(b)}} \left( S_{\vec{\theta}}(l_{j}^{(e)} - b + 1) - S_{\vec{\theta}}(r_{j}^{(e)} - b + 1) \right) \prob \left(B_{j} = b \right) &\text{by def of $S_{\vec{\theta}}$} \\
\propto& \sum_{b = l_{j}^{(b)}}^{r_{j}^{(b)}} \left( S_{\vec{\theta}}(l_{j}^{(e)} - b + 1) - S_{\vec{\theta}}(r_{j}^{(e)} - b + 1) \right)
\end{align}
under the assumption of uniform probability of infection time.
This is the standard form of the likelihood for doubly interval censored data without truncation.

>>>>

By definition (see \cpageref{perf-test:def:admissible}), we have, for any $i \in \set{D}$:
\begin{align}
p_{ia} =& \prob((B_j, E_j) \in \alpha_i \mid \vec{\theta}, i(j) = i) \\
\alpha_i =& \{ (b, e) : l_{j}^{(b)} \leq b \leq r_{j}^{(b)} \wedge l_{j}^{(e)} \leq e \leq r_{j}^{(e)}\}.
\intertext{Omitting the conditioning on $\vec{\theta}$ and $i(j) = i$, this gives:}
p_{ia}
=& \prob \left( l_{j}^{(b)} \leq B_{j} \leq r_{j}^{(b)}, l_{j}^{(e)} \leq E_{j} \leq r_{j}^{(e)} \right) \\
=& \prob \left( l_{j}^{(e)} \leq E_{j} \leq r_{j}^{(e)} \mid l_{j}^{(b)} \leq B_{j} \leq r_{j}^{(b)} \right) \\
   &\times\prob \left( l_{j}^{(b)} \leq B_{j} \leq r_{j}^{(b)} \right) \\
=& \sum_{b = l_{j}^{(l)}}^{r_{j}^{(b)}} \prob \left( l_{j}^{(e)} \leq E_{j} \leq r_{j}^{(e)} \mid B_{j} = b \right) \prob \left(B_{j} = b \right) \\
=& \sum_{b = l_{j}^{(b)}}^{r_{j}^{(b)}} \prob \left( l_{j}^{(e)} - b + 1 \leq D_{j} \leq r_{j}^{(e)} - b + 1 \right) \prob \left(B_{j} = b \right) &\text{by def of $D_{j}$} \\
=& \sum_{b = l_{j}^{(b)}}^{r_{j}^{(b)}} \left( S_{\vec{\theta}}(l_{j}^{(e)} - b + 1) - S_{\vec{\theta}}(r_{j}^{(e)} - b + 2) \right) \prob \left(B_{j} = b \right) &\text{by def of $S_{\vec{\theta}}$} \\
\propto& \sum_{b = l_{j}^{(b)}}^{r_{j}^{(b)}} \left( S_{\vec{\theta}}(l_{j}^{(e)} - b + 1) - S_{\vec{\theta}}(r_{j}^{(e)} - b + 2) \right)
\end{align}
under the assumption of uniform probability of infection time.
This is the standard form of the likelihood for doubly interval censored data without truncation.
